The Astropy Project: Building an open-science project and status of the v2.0 core package

### 2018-03-02 main.tex
Update main.tex
Fix for broken build

Additionally, there is now interoperability between \texttt{Table}
and \package{pandas} \texttt{DataFrame} objects using the \texttt{Table.to_pandas()}
and \texttt{Table.from_pandas()} methods. \texttt{Table.to_pandas()} is,
however, limited to a subset of possible \texttt{Table} objects, because several
of the features outlined above cannot be represented as \package{pandas} data
frames. While these features might be contributed to or combined with
\package{pandas} at a later date, the architectural differences that
enable these areas are significant, so this would be a major undertaking that would 
require substantial investment from the core maintainers and communities of both 
packages.

>>>>

Additionally, there is now interoperability between \texttt{Table}
and \package{pandas} \texttt{DataFrame} objects using the \texttt{Table.to\_pandas()}
and \texttt{Table.from\_pandas()} methods. \texttt{Table.to\_pandas()} is,
however, limited to a subset of possible \texttt{Table} objects, because several
of the features outlined above cannot be represented as \package{pandas} data
frames. While these features might be contributed to or combined with
\package{pandas} at a later date, the architectural differences that
enable these areas are significant, so this would be a major undertaking that would 
require substantial investment from the core maintainers and communities of both 
packages.
